NFL Draft Analysis

### 2020-05-10 draft_analysis.Rmd
Making Github Pages happy - moving index.html file into parent dir

---
title: 'NFL Draft Analysis'
author: "Philip Ipe"
date: "5/8/2020"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

>>>>

---
title: 'NFL Draft Analysis'
author: "Philip Ipe"
date: "5/8/2020"
output: html_document
knit: (function(input_file, encoding) {
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), 'index.html'))})
---
